---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
```


```{r}
UnemploymentCanada <- read_csv("Unemployment_Canada_1976_present.csv")

DataDictionary <- data.frame(
  VariableName = names(UnemploymentCanada),
  ReadableVariableName = c(
    "DATE", "REGION", "SEX", "AGE",
    "EMP", "EMP_FT", "LAB_FORCE",
    "EMP_PT", "POP", "UNEMP",
    "EMP_RATE", "PART_RATE", "UNEMP_RATE"
  ),
  MeasurementUnits = c(
    "YYYY-MM", "Category", "Category", "Category",
    "Numeric", "Numeric", "Numeric",
    "Numeric", "Numeric", "Numeric",
    "Percentage", "Percentage", "Percentage"
  ),
  AllowedValues = c(
    "1976-01 to 2023-01", 
    "All Canadian provinces and territories", 
    "Male, Female, Both Sexes", 
    "15 to 24 years, 15 to 64 years, 15 years and over, 25 to 54 years, 25 years and over, 55 years and over, 15 to 19 years, 20 to 24 years, 55 to 64 years",
    "0 - 10,000,000", 
    "0 - 10,000,000", 
    "0 - 10,000,000", 
    "0 - 10,000,000", 
    "0 - 10,000,000", 
    "0 - 10,000,000", 
    "0.0 - 100.0", 
    "0.0 - 100.0", 
    "0.0 - 100.0"
  ),
  VariableDefinitionFromSource = c(
    "The reference period (by year, month).",
    "The geographic area.",
    "The sex being investigated.",
    "The age group of the economic measure.",
    "Number of persons who, during the reference week, worked for pay or profit, or performed unpaid family work or had a job but were not at work due to own illness or disability, personal or family responsibilities, labour dispute, vacation, or other reason.",
    "Full-time employment consists of persons who usually work 30 hours or more per week at their main or only job.",
    "Number of civilian, non-institutionalized persons 15 years of age and over who, during the reference week, were employed or unemployed.",
    "Part-time employment consists of persons who usually work less than 30 hours per week at their main or only job.",
    "Number of persons of working age, 15 years and over.",
    "Number of persons who, during the reference week, were without work, had looked for work in the past four weeks, and were available for work. Those persons on layoff or who had a new job to start in four weeks or less are considered unemployed.",
    "The employment rate is the number of persons employed expressed as a percentage of the population 15 years of age and over.",
    "The participation rate is the number of labour force participants expressed as a percentage of the population 15 years of age and over.",
    "The unemployment rate is the number of unemployed persons expressed as a percentage of the labour force."
  ),
  stringsAsFactors = FALSE
)

print(DataDictionary)

write.csv(DataDictionary, "DataDictionary.csv", row.names = FALSE)

print("Data dictionary saved successfully as DataDictionary.csv")



```

## The data is compiled on a monthly basis by the Statistics Canada organization/website.

## I am particularly interested in this dataset because I love travelling, and learning about other countries' statistics is fascinating to me. I like to compare the data to that of the United States and look for the biggest similarities and differences, and think of reasoning for the discrepancies. 

## The dataset and variable definitions come from https://www.kaggle.com/datasets/pienik/unemployment-in-canada-by-province-1976-present

